---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
library(readxl)
library(stringr)
library(naniar)
library(janitor)
```

```{r}
clean_15 <- read_csv("clean_data/clean_main_15.csv")
clean_16 <- read_csv("clean_data/clean_main_16.csv")
clean_17 <- read_csv("clean_data/clean_main_17.csv")

main_15 <- clean_15
main_16 <- clean_16
main_17 <- clean_17
main_tot <- bind_rows(main_15, main_16) %>%
  bind_rows(main_17)
```


## Task 4 - Question 1 - What is the total number of candy ratings given across 
## the three years (Exclud. NAs)
```{r}
Cand_count_2015 <- sum(!is.na(main_15[7:ncol(main_15)]))
Cand_count_2016 <- sum(!is.na(main_16[7:ncol(main_16)]))
Cand_count_2017 <- sum(!is.na(main_17[7:ncol(main_17)]))
Cand_count = Cand_count_2015+Cand_count_2016+Cand_count_2017
Cand_count
```

## Task 4 - Question 2 - What was the average age of people who are going out 
## trick or treating and the average age of people not going trick or treating?

```{r}
tri_o_tre_15 <- select(main_15, c(going_out, age))
tri_o_tre_16 <- select(main_16, c(going_out, age))
tri_o_tre_17 <- select(main_17, c(going_out, age))

tri_o_tre_tot <- rbind(tri_o_tre_17, tri_o_tre_16)
  tri_o_tre_tot <- rbind (tri_o_tre_tot, tri_o_tre_15) %>% 
  group_by(going_out) %>%
  summarise(avg_age = mean(age, na.rm = TRUE)) 
  
names(tri_o_tre_tot)[names(tri_o_tre_tot)== "going_out"] <- "going_out_trick_or_treat"
tri_o_tre_tot
```
## Task 4 - Question 3 - How many people rated Starburst as despair?

```{r}
# Checking what are the difference in column names in the 3 dataframes.
# diff_colnam <- compare_df_cols(main_15, main_16, main_17, return = "match") 
names(main_17)[names(main_17)== "anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes"] <- "anonymous_brown_globs_that_come_in_black_and_orange_wrappers"
names(main_17)[names(main_17)== "100_grand_bar"] <- "x100_grand_bar"
names(main_15)[names(main_15)== "box_o_raisins"] <- "boxo_raisins"


#Merge Dataframes
main_tot <- merge(main_17, main_16, all = TRUE)
main_tot <- merge(main_tot, main_15, all = TRUE)

rating_count <- main_tot[4:ncol(main_tot)] %>% 
  summarise_all(~ sum(!is.na(.)))

rating_count <- as.data.frame(t(rating_count))

#extract rownames then join rating_count as column
sweet_name <- str_to_title(rownames(rating_count))
rownames(rating_count) <- NULL
rating_count <- cbind(sweet_name, rating_count)

#remove rowname


colnames(rating_count)[1] <- "sweet_name"
colnames(rating_count)[2] <- "rating"

Max_rating_sweet <- slice_max(rating_count, rating)
Max_rating_sweet
```

## Task 4 - Question 4 - How many people rated Starburst as despair?
```{r}
star_despair <- main_tot %>% 
    filter(starburst == "DESPAIR")

nrow(star_despair)
```


## For the next three questions, count despair as -1, joy as +1 and meh as 0.
## Task 4 - Question 6 - What was the most popular candy bar by this rating system for each gender in the dataset?
```{r}
rating_tot <- main_tot %>%
  select(-c(year, going_out, age, country)) %>%
  group_by(gender) %>%
  summarise(across(where(.,"JOY")),na.rm = TRUE)

# rating_joy <- rating_tot
# 
# for(y in 2:ncol(rating_joy)) {
#   for (z in 1:nrow(rating_joy)) {
#     rating_joy[z, y] <-
#       lapply(rating_joy[z, y], function(x)
#         replace(x, x != "JOY", NA))
#   }
# }



```

